R-LIME: Rectangular Constraints and Optimization for Local Interpretable Model-agnostic Explanation Methods\thanks{Supported by organization x.}

### 2024-02-09 paper.tex
Add submodule MyRef and work on paper

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%
\begin{document}
%
\title{Contribution Title\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc.\ does not need an indent, either.

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%
\begin{document}
%
\title{R-LIME: Rectangular Constraints and Optimization for Local Interpretable
Model-agnostic Explanation Methods\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Genji Ohara\inst{1}\orcidID{0000-1111-2222-3333} \and
Keigo Kimura\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Mineichi Kudo\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{G. Ohara et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
% The abstract should briefly summarize the contents of the paper in
% 150--250 words.
\begin{abstract}
    In recent years, complex machine learning models such as deep neural network or random forests are used in many situations because of their high accuracy.
    However, complexity of the models leads to difficulty for introducing them in sensitive context because users cannot understand the reason why the models output the specific results.
    We propose a new method to generate explanations about the complex classifier and its particular output, that is called R-LIME.
    R-LIME approximizes a complex decision boundary by a linear classifier locally and maximizes the approximation region as long as the accuracy of the linear model is higher than given threshold.
% 102 words
\keywords{Interpretable machine learning \and Local surrogate model}
\end{abstract}

\section{Introduction}
In recent years, complex machine learning models such as deep neural network or random forests are used in many situations because of their high accuracy.
However, complexity of the models leads to difficulty for introducing them in sensitive context because users cannot understand the reason why the models output the specific results.
To solve this problem, many explanation methods have been proposed.

In this paper, we focus on local and model-agnostic explanation methods.
LIME (Local Interpretable Model-agnostic Explanation) \cite{ribeiro2016why} is one of the most popular explanation methods.
LIME approximizes a complex decision boundary by a linear classifier locally.
But users cannot evaluate generality of LIME explanations because it does not provide the approximation region.
To solve this problem, we propose a new method, R-LIME.
R-LIME approximizes a complex decision boundary by a linear classifier locally and maximizes the approximation region as long as the accuracy of the linear model is higher than given threshold.
Moreover, R-LIME provides the approximation region as conjunction of predicates, that is called anchor \cite{ribeiro2018anchors}.
\section{Related Works}
\subsection{LIME}
\subsection{Anchor}
\subsection{BELLA}
\section{Proposed Method}
\subsection{Overview}
\subsection{Algorithm}
\section{Experiments}
\subsection{Qualitative Evaluation}
\subsection{Quantitative Evaluation}
\section{Future Works}
\section{Conclusion}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc.\ does not need an indent, either.

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{MyRef/ref}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
